### 2012-06-28 inst/examples/bh_lognormal.Rmd
bh lognormal queued on zero

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_uniform_fast/", verbose=TRUE or`

@@

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.

@@

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bh_lognormal/", verbose=TRUE or`

@@

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.005`.

@@

  z_g <- function() rlnorm(1,0, policy_g)
  z_m <- function() rlnorm(1,0, policy_m)
  z_i <- function() rlnorm(1,0,policy_i)
